### 2023-02-07 saturation-ver3/kt-formula-report1/kt-formula-report1.tex
large x problematic

>>>>

\section{Computational strategies}
\subsection{$\alpha\mathcal{F}$ and $\nabla^2_r \sigma$}
\begin{equation}
\begin{split}
\alpha\mathcal{F}&=\frac{3}{8\pi^2}\int^\infty_0dr r J_0(r k)\nabla^2_r \sigma(x,r)\\
&=\frac{3}{8\pi^2}\int^\infty_0dr rJ_0(r k) \left(\frac{1}{r}\frac{\partial}{\partial r}\left(r\frac{\partial}{\partial r}\right)\right) \sigma(x,r)
\end{split}
\end{equation}
Using integration by parts,
\begin{equation}
\begin{split}
\alpha\mathcal{F}&=\frac{3}{8\pi^2}\int^\infty_0dr J_0(r k) \frac{\partial}{\partial r} \left(r\frac{\partial}{\partial r}\right) \sigma(x,r)\\
&=\frac{3}{8\pi^2}\left[ J_0(r k)\left(r\frac{\partial}{\partial r}\right) \sigma(x,r) - \int dr \frac{\partial J_0(r k)}{\partial r} \left(r\frac{\partial}{\partial r}\right) \sigma(x,r)\right]^\infty_0\\
&=\frac{3}{8\pi^2}\left[  \int dr r k J_1(r k)\frac{\partial}{\partial r}\sigma(x,r)\right]^\infty_0,
\end{split}
\end{equation}
assuming 
\begin{equation}
\lim_{r\rightarrow0,\infty}J_0(r k)\left(r\frac{\partial}{\partial r}\right) \sigma(x,r)=0.
\end{equation}
Hence, one has two ways to compute the gluon density;
\begin{align}
&\frac{3}{8\pi^2}\int^\infty_0dr r J_0(r k)\nabla^2_r \sigma(x,r)\\
&\frac{3}{8\pi^2}\int^\infty_0  dr r k J_1(r k)\frac{\partial}{\partial r}\sigma(x,r)
\end{align}
Now, these integrals are in the form of\textbf{ Hankel transform}.

as a by-product of interpolation, derivatives are obtainable in gsl\_cheb or gsl\_interp. However in any case second derivative may become a source of inaccuracy...

Let us assume small $Q_s^2$, and for $r>>Q_s$, integrand is negligible, then
\begin{equation}
\begin{split}
\frac{3}{8\pi^2}\int^{1/Q_s}_0  dr r k J_1(r k)\frac{\partial}{\partial r}\sigma(x,r)\\
\simeq \frac{3}{8\pi^2}\int^{1/Q_s}_0  dr  k J_1(r k) r^2 Q_s^2\\
=\frac{3Q_s^2}{8\pi^2} \frac{J_2(k/Q_s)}{k Q_s^2}  
\end{split}
\end{equation}
